\documentclass[12pt]{article}
\usepackage{latexsym}
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{tikz}

\topmargin = 0.1in \textwidth=5.7in \textheight=8.6in

\oddsidemargin = 0.2in \evensidemargin = 0.2in


\begin{document}

\begin{center}
COMPUTER SCIENCE 20, SPRING 2014 \\
Homework Problems\\
Strong Induction, Propositional Logic
\end{center}

\smallskip


\paragraph*{Due Wednesday February 12, 2014. CS 20 students should bring a hard copy to class. CSCI E-120 students should submit an electronic copy.} 


\begin{enumerate}

\item Suppose you are given a real number $x$ such that $x + \frac{1}{x}$ is an integer.  Use Strong Induction to show that $x^n + \frac{1}{x^n}$ is an integer for all positive integers $n$.

\item[ ] {\bf Solution}: For $n=1$, the result holds. For $n=2$, we know that $(x+\frac{1}{x})^2 =x^2 + \frac{1}{x^2} + 2$, so the result holds for $n=2$. Suppose the result holds for all positive integers $n<k$. The induction hypothesis tells us $x^{k-1}+\frac{1}{x^{k-1}}$ is an integer. Moreover, we know $x+\frac 1 x$ is an integer, so we conclude:
\begin{eqnarray*}
(x^{k-1}+\frac{1}{x^{k-1}})(x+\frac 1 x) &=& x^k + \frac{x^{k-1}}{x}+\frac{x}{x^{k-1}} + \frac{1}{x^k}\\
&=&x^k+\frac{1}{x^k} + x^{k-2} + \frac{1}{x^{k-2}}
\end{eqnarray*}
Given that the induction hypothesis guarantees $x^{k-2} + \frac{1}{x^{k-2}}$ is an integer, it follows that  $x^k + \frac 1 {x^k}$ is an integer.

\textbf{Question: } \\
The solution is a little bit unclear to me if we plug $2$ into this equation, this is what I see as the result. $x^2 + \frac{1}{x^2}$ In your solution I see that
you have an extra $+2$, not sure where that is comming from as it does not seem obvious to me. Also I noticed that you used $k-1$ in ypur inductive hypothesis
why is that? I thought that were always trying to prove for $n+1$



\end{enumerate}

\pagebreak




















\end{document}
